Model Samples Processing

### 2020-02-13 stats/model_comparison.Rmd
update model sample processing file

# Model comparison

@@

>>>>

# Model comparison prediction

@@

# Model comparison explanation

model_like <- bind_rows(

  readRDS("../saves/model_pred_prag_fb.rds") %>%
    mutate(model = "fullBayes")%>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)

    # ,readRDS("../saves/model_pred_mm.rds") %>%
    # mutate(model = "mixture")%>%
    # right_join(d_model_comp.summarized)%>%
    # select(model,chain,iteration, age, alignment,item,pred, n, k)
) %>%
  mutate(
    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
  ) %>%
  group_by(chain, model, iteration) %>%
  summarize(total_likelihood_sample = sum(log_like))

# variation across chains

model_by_chain <- model_like %>%
  na.omit(chain)%>%
  group_by(model, chain) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)

# compare models
model_comp <- model_like %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)%>%
  mutate(fb_vs_free = fullBayes - pragmatic
         # ,fb_vs_mixture= fullBayes - mixture,
         # free_vs_mixture = pragmatic - mixture
         ) %>%
  select(-pragmatic, -fullBayes, -mixture) %>%
  gather(model, logBF)

### 2020-02-13 stats/model_sample_processing.Rmd
update model sample processing file

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "pragmatic")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

>>>>

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "pragmatic")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g,
         model = "fullBayes")
